### 2017-05-12 hdf5_data_doc.tex
trying out stuff in the tryin file. Tex of documentation of  coversion script.

\title{Documentation of Calcium Imaging Data, Converted to HDF5}

\documentclass[12pt]{article}

\usepackage{listings}

\begin{document}
\maketitle
First, install the h5py package if it is not installed already. If you are using anaconda, do
\begin{lstlisting}
conda install h5py
\end{lstlisting}
Otherwise
\begin{lstlisting}
pip install h5py
\end{lstlisting}
To access the data of a file with the name "140708B\_140811a\_result.hdf5", write:

\begin{lstlisting}[language=Python]
import h5py

filename = "calcium_data/140708B_140811a_result.hdf5"
f = h5py.File(filename, "r")
\end{lstlisting}
This loads the .hdf5 file into f.

Each such file contains three datasets, "meta", "data" and "licktimes" (it is assumed that the files are contained in the folder "calcium\_data" that is located in the same folder as this script. Adjust accordingly.). The file is automatically closed when the script terminates. In ipython notebook it can sometimes be necessary to restart the kernel if one wants to reload the data, as it keeps its variables in memory and does not "terminate" the program. To access a dataset, do:
\begin{lstlisting}[language=Python]
meta = f['meta']			#or
data = f['data']			#or
licktimes = f['licktimes']
\end{lstlisting}
These datasets, now contained in meta, data and licktimes function very much the same way as numpy arrays. The most notable difference is that if we want to access the whole dataset, we write (for example)
\begin{lstlisting}[language=Python]
print(data[:])
\end{lstlisting}
instead of
\begin{lstlisting}[language=Python]
print(data)
\end{lstlisting}
as the latter will only return some properties of the dataset. There are other small differences that are not likely to be important (for example fancy indexing can be slow). \newline

\begin{lstlisting}[language=Python]
f['meta']
\end{lstlisting}
is an array of shape (n\_trials, 3) and contains, in this order the values session, stimAmp and hit/miss for every trial. A "hit" is encoded by a 1, while a "miss" is encoded by a 0. To find out whether trial 75 was a hit or a miss, we write
\begin{lstlisting}[language=Python]
meta = f['meta']
print(meta[75,2])
>>>1
\end{lstlisting}
which means, that this trial is a "hit". \newline

\begin{lstlisting}[language=Python]
f['data']
\end{lstlisting}
is an array with shape (n\_trials, n\_recordSites, n\_times).
\begin{lstlisting}[language=Python]
data = f['data']
print(data[75, 5,:])
\end{lstlisting}
will print the timeseries of the calcium imaging from trial 75 and recording site 5. \newline

\begin{lstlisting}[language=Python]
f['licktimes']
\end{lstlisting}
is an array of shape (n\_trials, max\_licktimes) which contains the licktimes for every trial. Its second dimension is equal to the maximum number of licktimes recorded for that file. Writing
\begin{lstlisting}[language=Python]
licktimes = f['licktimes']
print(licktimes[75,:])
\end{lstlisting}
will print out the licktimes for trial 75. A "-1" signifies a dummy value and can be ignored.

\end{document}
This is never printed

### 2017-07-07 presentation/demo.tex
asd

\documentclass[10pt]{beamer}

\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\title{Multivariate Analysis of Dendritic Ca2+ Data}
\subtitle{In a Stimulus Detection Task}
\date{\today}
%\date{}
\author{Georg Chechelnizki}
\institute{BCCN Berlin}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

\setbeamercolor{background canvas}{bg=white}
\usepackage{caption}

\begin{document}

\maketitle

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents[hideallsubsections]
\end{frame}

\section{Introduction}

\begin{frame}[fragile]{The Experiment}
\begin{columns}[T,onlytextwidth]
    \column{0.5\textwidth}
    	\only<+->{
      \begin{figure}
      \includegraphics[scale=0.1]{mouse.png}
      \end{figure}}

    \column{0.5\textwidth}
		\only<+->{
      \begin{figure}
      \includegraphics[scale=0.1]{roi.png}
      \end{figure}}

  \end{columns}
\end{frame}

\begin{frame}[fragile]{The Data - Neuronal}
	\begin{center}
	\begin{figure}
	\caption*{Trial-averaged $\text{Ca}^{2+}$ fluorescence traces of random dendrites}
      \includegraphics[scale=0.35]{traces.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{The Data - Behavioral}
	\begin{center}
	\begin{figure}
      \includegraphics[scale=0.23	]{lickplots.png}
	\end{figure}
	\end{center}
\end{frame}

\section{What Has Happened So Far - Univariate Analysis}

\begin{frame}{Psychometric Curve}
\begin{center}
	\begin{figure}
      \includegraphics[scale=0.38]{psychometric.png}
	\end{figure}
	\end{center}

\end{frame}

\begin{frame}{ROC-Analysis}
\begin{center}
	\begin{figure}
      \includegraphics[width=0.75\textwidth]{roc_max.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{DI-Histograms}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{DI_hist.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{$\text{Ca}^{2+}$-Trace of Largest $|\text{DI}|$-Dendrites}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{on_vs_off.png}
      \caption*{Near threshold-stimulus ($\approx 1$)}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}
placeholder SI-stuff
\end{frame}

\section{Titleformats}

\begin{frame}{Metropolis titleformats}
	\themename supports 4 different titleformats:
	\begin{itemize}
		\item Regular
		\item \textsc{Smallcaps}
		\item \textsc{allsmallcaps}
		\item ALLCAPS
	\end{itemize}
	They can either be set at once for every title type or individually.
\end{frame}

{
    \metroset{titleformat frame=smallcaps}
\begin{frame}{Small caps}
	This frame uses the \texttt{smallcaps} titleformat.

	\begin{alertblock}{Potential Problems}
		Be aware, that not every font supports small caps. If for example you typeset your presentation with pdfTeX and the Computer Modern Sans Serif font, every text in smallcaps will be typeset with the Computer Modern Serif font instead.
	\end{alertblock}
\end{frame}
}

{
\metroset{titleformat frame=allsmallcaps}
\begin{frame}{All small caps}
	This frame uses the \texttt{allsmallcaps} titleformat.

	\begin{alertblock}{Potential problems}
		As this titleformat also uses smallcaps you face the same problems as with the \texttt{smallcaps} titleformat. Additionally this format can cause some other problems. Please refer to the documentation if you consider using it.

		As a rule of thumb: Just use it for plaintext-only titles.
	\end{alertblock}
\end{frame}
}

{
\metroset{titleformat frame=allcaps}
\begin{frame}{All caps}
	This frame uses the \texttt{allcaps} titleformat.

	\begin{alertblock}{Potential Problems}
		This titleformat is not as problematic as the \texttt{allsmallcaps} format, but basically suffers from the same deficiencies. So please have a look at the documentation if you want to use it.
	\end{alertblock}
\end{frame}
}

\section{Elements}

\begin{frame}[fragile]{Typography}
      \begin{verbatim}The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.\end{verbatim}

  \begin{center}becomes\end{center}

  The theme provides sensible defaults to \emph{emphasize} text,
  \alert{accent} parts or show \textbf{bold} results.
\end{frame}

\begin{frame}{Font feature test}
  \begin{itemize}
    \item Regular
    \item \textit{Italic}
    \item \textsc{SmallCaps}
    \item \textbf{Bold}
    \item \textbf{\textit{Bold Italic}}
    \item \textbf{\textsc{Bold SmallCaps}}
    \item \texttt{Monospace}
    \item \texttt{\textit{Monospace Italic}}
    \item \texttt{\textbf{Monospace Bold}}
    \item \texttt{\textbf{\textit{Monospace Bold Italic}}}
  \end{itemize}
\end{frame}

\begin{frame}{Lists}
  \begin{columns}[T,onlytextwidth]
    \column{0.33\textwidth}
      Items
      \begin{itemize}
        \item Milk \item Eggs \item Potatos
      \end{itemize}

    \column{0.33\textwidth}
      Enumerations
      \begin{enumerate}
        \item First, \item Second and \item Last.
      \end{enumerate}

    \column{0.33\textwidth}
      Descriptions
      \begin{description}
        \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
      \end{description}
  \end{columns}
\end{frame}
\begin{frame}{Animation}
  \begin{itemize}[<+- | alert@+>]
    \item \alert<4>{This is\only<4>{ really} important}
    \item Now this
    \item And now this
  \end{itemize}
\end{frame}
\begin{frame}{Figures}
  \begin{figure}
    \newcounter{density}
    \setcounter{density}{20}
    \begin{tikzpicture}
      \def\couleur{alerted text.fg}
      \path[coordinate] (0,0)  coordinate(A)
                  ++( 90:5cm) coordinate(B)
                  ++(0:5cm) coordinate(C)
                  ++(-90:5cm) coordinate(D);
      \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
      \foreach \x in {1,...,40}{%
          \pgfmathsetcounter{density}{\thedensity+20}
          \setcounter{density}{\thedensity}
          \path[coordinate] coordinate(X) at (A){};
          \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
                              -- (C) coordinate[pos=.10](B)
                              -- (D) coordinate[pos=.10](C)
                              -- (X) coordinate[pos=.10](D);
          \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
      }
    \end{tikzpicture}
    \caption{Rotated square from
    \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
  \end{figure}
\end{frame}
\begin{frame}{Tables}
  \begin{table}
    \caption{Largest cities in the world (source: Wikipedia)}
    \begin{tabular}{lr}
      \toprule
      City & Population\\
      \midrule
      Mexico City & 20,116,842\\
      Shanghai & 19,210,000\\
      Peking & 15,796,450\\
      Istanbul & 14,160,467\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}
\begin{frame}{Blocks}
  Three different block environments are pre-defined and may be styled with an
  optional background color.

  \begin{columns}[T,onlytextwidth]
    \column{0.5\textwidth}
      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

    \column{0.5\textwidth}

      \metroset{block=fill}

      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

  \end{columns}
\end{frame}
\begin{frame}{Math}
  \begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
  \end{equation*}
\end{frame}
\begin{frame}{Line plots}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mlineplot,
        width=0.9\textwidth,
        height=6cm,
      ]

        \addplot {sin(deg(x))};
        \addplot+[samples=100] {sin(deg(2*x))};

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Bar charts}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mbarplot,
        xlabel={Foo},
        ylabel={Bar},
        width=0.9\textwidth,
        height=6cm,
      ]

      \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
      \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
      \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};

      \legend{lorem, ipsum, dolor}

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Quotes}
  \begin{quote}
    Veni, Vidi, Vici
  \end{quote}
\end{frame}

{%
\setbeamertemplate{frame footer}{My custom footer}
\begin{frame}[fragile]{Frame footer}
    \themename defines a custom beamer template to add a text to the footer. It can be set via
    \begin{verbatim}\setbeamertemplate{frame footer}{My custom footer}\end{verbatim}
\end{frame}
}

\begin{frame}{References}
  Some references to showcase [allowframebreaks] \cite{knuth92,ConcreteMath,Simpson,Er01,greenwade93}
\end{frame}

\section{Conclusion}

\begin{frame}{Summary}

  Get the source of this theme and the demo presentation from

  \begin{center}\url{github.com/matze/mtheme}\end{center}

  The theme \emph{itself} is licensed under a
  \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
  Attribution-ShareAlike 4.0 International License}.

  \begin{center}\ccbysa\end{center}

\end{frame}

{\setbeamercolor{palette primary}{fg=black, bg=yellow}
\begin{frame}[standout]
  Questions?
\end{frame}
}

\appendix

\begin{frame}[fragile]{Backup slides}
  Sometimes, it is useful to add slides at the end of your presentation to
  refer to during audience questions.

  The best way to do this is to include the \verb|appendixnumberbeamer|
  package in your preamble and call \verb|\appendix| before your backup slides.

  \themename will automatically turn off slide numbering and progress bars for
  slides in the appendix.
\end{frame}

\begin{frame}[allowframebreaks]{References}

  \bibliography{demo}
  \bibliographystyle{abbrv}

\end{frame}

\end{document}

### 2017-07-07 ROC.py

@@ -76,13 +76,16 @@ def get_DIs(filename, amp, permute=False):
     data = f['data']
     meta = f['meta']
     
+    g = h5py.File(filename[:-6]+"roi.hdf5", "r")
+    motion_mask = (g['inFrameDend'][:].astype(bool)).reshape(g['inFrameDend'].shape[0])
+    
     stims = np.unique(h5py.File(filename+".hdf5", "r")['meta'][:,1])[1:]
     
     assert(amp in list(stims)), "this stimAmp was not used in chosen experiment. Cose one from {}.".format(stims)
 
-    baseline = np.mean(data[:,:,:58], axis=2).reshape(data.shape[0], data.shape[1], 1)
+    baseline = np.mean(data[:,motion_mask,:58], axis=2).reshape(data.shape[0], np.sum(motion_mask), 1)
 
-    mn_dnd_chng = np.mean(data[:,:,58:116]-baseline, axis=2)
+    mn_dnd_chng = np.mean(data[:,motion_mask,58:116]-baseline, axis=2)
 
     present_mask = meta[:,1]==amp
     absent_mask = meta[:,1]==0
@@ -95,8 +98,52 @@ def get_DIs(filename, amp, permute=False):
         y_true = np.random.permutation(y_true)
     
     DIs = []
-    for site in range(data.shape[1]):
+    for site in range(np.sum(motion_mask)):
         y_score = mn_dnd_chng[trials_mask, site]
     
         DIs.append((roc_auc_score(y_true, y_score)-0.5)*2)
     return DIs
+
+def get_DIs_psycho(filename, amp, permute=False):
+    f = h5py.File(filename+".hdf5", "r")
+    
+    #average delta F
+    #1s = 59 frames
+    data = f['data']
+    meta = f['meta']
+    
+    g = h5py.File(filename[:-6]+"roi.hdf5", "r")
+    motion_mask = (g['inFrameDend'][:].astype(bool)).reshape(g['inFrameDend'].shape[0])
+    
+    stims = np.unique(h5py.File(filename+".hdf5", "r")['meta'][:,1])[:]
+    
+    assert(amp in list(stims)), "this stimAmp was not used in chosen experiment. Cose one from {}.".format(stims)
+
+    baseline = np.mean(data[:,motion_mask,:58], axis=2).reshape(data.shape[0], np.sum(motion_mask), 1)
+
[…]

### 2017-07-07 polynomial.py

@@ -1,0 +1,81 @@
+import numpy as np
+import h5py
+
+def fit_polynomial(filename, deg=6, exclude_mask=None):
+    '''
+    returns: ndarray of shape (deg+1, n_trials, n_dendrites)
+    '''
+    f = h5py.File(filename+'.hdf5', 'r')
+    
+    data = f['data']
+    meta = f['meta']
+    
+    n_trials = data.shape[0]
+    n_dendrites = data.shape[1]
+    
+    if exclude_mask:
+        #remove unwanted trials
+        pass
+    
+    coef_mat = np.zeros((deg+1, n_trials, n_dendrites))
+    for i in range(n_trials):
+        x = np.arange(0,180)
+        y = data[i,:,:]
+
+        coef = np.polynomial.polynomial.polyfit(x,y.T,deg)
+        coef_mat[:, i, :] = coef
+        
+    return coef_mat
+
+def get_poly_time(coef):
+    '''
+    returns: ndarray of shape (n_trials, n_dendrites, n_times)
+    '''
+    x = np.arange(0, 180)
+    p = np.polynomial.polynomial.polyval(x, coef)
+    
+    return p
+
+def get_feature_matrix(coef):
+    '''
+    returns: ndarray of shape (n_trials, (n_coef*n_dendrites)), with every row being (p0_all_dends, ..., p_n_all_dends)
+    '''
+    n_coef = coef.shape[0]
+    n_trials = coef.shape[1]
+    n_dendrites = coef.shape[2]
+    
+    X = np.zeros((n_trials, n_dendrites*n_coef))
+    for i in range(n_trials):
+        mat = coef[:,i,:]
+        #print(mat.shape)
+        for j in range(n_dendrites):
+            #print(X[i, j*n_coef:(j+1)*n_coef].shape)
+            X[i, j*n_coef:(j+1)*n_coef] = mat[:,j]
+            
+    return X
+
+def get_orig_matrix(X, deg):
+    n_trials = X.shape[0]
+    print(X.shape)
+    n_dendrites = X.shape[1]/(deg+1)
+    assert(n_dendrites%1 == 0)
+    n_dendrites = int(n_dendrites)
+    
+    data = np.zeros((deg+1, n_trials, n_dendrites))
+    for i in range(n_trials):
+        for j in range(n_dendrites):
+            data[:, i, j] = X[i,j*(deg+1):(j+1)*(deg+1)]
+    
+    return data
+
[…]

### 2017-07-12 presentation/demo.tex
asd

@@
 
-\title{Multivariate Analysis of Dendritic Ca2+ Data}
+\title{Uni- and Multivariate Analysis of Dendritic Ca2+ Data}
 \subtitle{In a Stimulus Detection Task}
@@
 
-\section{What Has Happened So Far - Univariate Analysis}
-
-\begin{frame}{Psychometric Curve}
+\begin{frame}[fragile]{The Data - Psychometric Curve}
 \begin{center}
@@
 
-\begin{frame}{ROC-Analysis}
+\section{Goal}
+\begin{frame}[fragile]{Goal}
+The goal of this project is to investigate the following:
+\begin{itemize}
+\only<+->{
+\item What information can we extract from the data?}
+\only<+->{
+\item What can we gain by doing multivariate analysis as opposed to univariate?}
+\only<+->{
+\item Can we say something about population coding?}
+\end{itemize}
+\end{frame}
+
+\section{Univariate Analysis}
+
+\begin{frame}[fragile]{Stimulus Presence Detection}
+\begin{itemize}
+\item Feature: mean activity of dendrite over one second after stimulus
+\item Class one: all trials with stimulus strength 0
+\item Class two: all trials with selected stimulus strength $(\neq 0)$
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]{ROC}
 \begin{center}
@@
 
-\begin{frame}{DI-Histograms}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{DI_hist.png}
-	\end{figure}
-	\end{center}
-\end{frame}
+%\begin{frame}[fragile]{Distribution of DI-Values}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{DI_hist.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+%
+%\begin{frame}[fragile]{Distribution of DI-Values vs. Chance}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{realchance.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
 
-\begin{frame}{$\text{Ca}^{2+}$-Trace of Largest $|\text{DI}|$-Dendrites}
+\begin{frame}[fragile]{$\text{Ca}^{2+}$-Trace of Largest $|\text{DI}|$-Dendrites}
 \begin{center}
@@
 
-\begin{frame}
-placeholder SI-stuff
-\end{frame}
+%\begin{frame}[fragile]{ROC Scores of Single Dendrites Using SVM}
+%\begin{table}
+%    \caption*{Stimulus strength 1 (near thereshold). Something is fishy here}
+%    \begin{tabular}{c|c|c}
+%      \toprule
+%      Dendrite \# & Mean Accuracy & Standard Deviation\\
+%      \midrule
+%      57 & 0.44 & +/- 0.51\\
+%      53 & 0.40 & +/- 0.28\\
+%      48 & 0.38 & +/- 0.49\\
+%      2 & 0.37 & +/- 0.74\\
+%      \bottomrule
+%    \end{tabular}
+%  \end{table}
+%\end{frame}
 
-\section{Titleformats}
-
-\begin{frame}{Metropolis titleformats}
-	\themename supports 4 different titleformats:
-	\begin{itemize}
-		\item Regular
-		\item \textsc{Smallcaps}
-		\item \textsc{allsmallcaps}
-		\item ALLCAPS
-	\end{itemize}
-	They can either be set at once for every title type or individually.
-\end{frame}
-
-{
-    \metroset{titleformat frame=smallcaps}
-\begin{frame}{Small caps}
-	This frame uses the \texttt{smallcaps} titleformat.
-
-	\begin{alertblock}{Potential Problems}
-		Be aware, that not every font supports small caps.
-If for example you typeset your presentation with pdfTeX and the Computer Modern Sans Serif font, every text in smallcaps will be typeset with the Computer Modern Serif font instead.
-	\end{alertblock}
-\end{frame}
-}
-
-{
-\metroset{titleformat frame=allsmallcaps}
-\begin{frame}{All small caps}
-	This frame uses the \texttt{allsmallcaps} titleformat.
-
-	\begin{alertblock}{Potential problems}
-		As this titleformat also uses smallcaps you face the same problems as with the \texttt{smallcaps} titleformat.
-Additionally this format can cause some other problems.
-Please refer to the documentation if you consider using it.
-
-		As a rule of thumb: Just use it for plaintext-only titles.
-	\end{alertblock}
-\end{frame}
-}
-
-{
-\metroset{titleformat frame=allcaps}
-\begin{frame}{All caps}
-	This frame uses the \texttt{allcaps} titleformat.
-
-	\begin{alertblock}{Potential Problems}
-		This titleformat is not as problematic as the \texttt{allsmallcaps} format, but basically suffers from the same deficiencies. So please have a look at the documentation if you want to use it.
-	\end{alertblock}
-\end{frame}
-}
-
-\section{Elements}
-
-\begin{frame}[fragile]{Typography}
-      \begin{verbatim}The theme provides sensible defaults to
-\emph{emphasize} text, \alert{accent} parts
-or show \textbf{bold} results.\end{verbatim}
-
-  \begin{center}becomes\end{center}
-
-  The theme provides sensible defaults to \emph{emphasize} text,
-  \alert{accent} parts or show \textbf{bold} results.
-\end{frame}
-
-\begin{frame}{Font feature test}
-  \begin{itemize}
-    \item Regular
-    \item \textit{Italic}
-    \item \textsc{SmallCaps}
-    \item \textbf{Bold}
-    \item \textbf{\textit{Bold Italic}}
-    \item \textbf{\textsc{Bold SmallCaps}}
-    \item \texttt{Monospace}
-    \item \texttt{\textit{Monospace Italic}}
-    \item \texttt{\textbf{Monospace Bold}}
-    \item \texttt{\textbf{\textit{Monospace Bold Italic}}}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Lists}
-  \begin{columns}[T,onlytextwidth]
-    \column{0.33\textwidth}
-      Items
-      \begin{itemize}
-        \item Milk \item Eggs \item Potatos
-      \end{itemize}
-
-    \column{0.33\textwidth}
-      Enumerations
-      \begin{enumerate}
-        \item First, \item Second and \item Last.
-      \end{enumerate}
-
-    \column{0.33\textwidth}
-      Descriptions
-      \begin{description}
-        \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
-      \end{description}
-  \end{columns}
-\end{frame}
-\begin{frame}{Animation}
-  \begin{itemize}[<+- | alert@+>]
-    \item \alert<4>{This is\only<4>{ really} important}
-    \item Now this
-    \item And now this
-  \end{itemize}
-\end{frame}
-\begin{frame}{Figures}
-  \begin{figure}
-    \newcounter{density}
-    \setcounter{density}{20}
-    \begin{tikzpicture}
-      \def\couleur{alerted text.fg}
-      \path[coordinate] (0,0)  coordinate(A)
-                  ++( 90:5cm) coordinate(B)
-                  ++(0:5cm) coordinate(C)
-                  ++(-90:5cm) coordinate(D);
-      \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
-      \foreach \x in {1,...,40}{%
-          \pgfmathsetcounter{density}{\thedensity+20}
-          \setcounter{density}{\thedensity}
-          \path[coordinate] coordinate(X) at (A){};
-          \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
-                              -- (C) coordinate[pos=.10](B)
-                              -- (D) coordinate[pos=.10](C)
-                              -- (X) coordinate[pos=.10](D);
-          \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
-      }
-    \end{tikzpicture}
-    \caption{Rotated square from
-    \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
-  \end{figure}
-\end{frame}
-\begin{frame}{Tables}
+\begin{frame}[fragile]{SVM - Most Accurate Dendrites}
 \begin{table}
-    \caption{Largest cities in the world (source: Wikipedia)}
-    \begin{tabular}{lr}
+    \caption*{Stimulus strength 1 (near thereshold)}
+    \begin{tabular}{c|c|c}
       \toprule
-      City & Population\\
+      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
       \midrule
-      Mexico City & 20,116,842\\
-      Shanghai & 19,210,000\\
-      Peking & 15,796,450\\
-      Istanbul & 14,160,467\\
+      57 & 0.70 & 0.12\\
+      53 & 0.68 & 0.14\\
+      48 & 0.63 & 0.13\\
+      27 & 0.62 & 0.08\\
       \bottomrule
@@
 \end{frame}
-\begin{frame}{Blocks}
-  Three different block environments are pre-defined and may be styled with an
-  optional background color.
 
-  \begin{columns}[T,onlytextwidth]
-    \column{0.5\textwidth}
-      \begin{block}{Default}
-        Block content.
-      \end{block}
-
-      \begin{alertblock}{Alert}
-        Block content.
-      \end{alertblock}
-
-      \begin{exampleblock}{Example}
-        Block content.
-      \end{exampleblock}
-
-    \column{0.5\textwidth}
-
-      \metroset{block=fill}
-
-      \begin{block}{Default}
-        Block content.
-      \end{block}
-
-      \begin{alertblock}{Alert}
-        Block content.
-      \end{alertblock}
-
-      \begin{exampleblock}{Example}
-        Block content.
-      \end{exampleblock}
-
-  \end{columns}
-\end{frame}
-\begin{frame}{Math}
-  \begin{equation*}
-    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
-  \end{equation*}
-\end{frame}
-\begin{frame}{Line plots}
-  \begin{figure}
-    \begin{tikzpicture}
-      \begin{axis}[
-        mlineplot,
-        width=0.9\textwidth,
-        height=6cm,
-      ]
-
-        \addplot {sin(deg(x))};
-        \addplot+[samples=100] {sin(deg(2*x))};
-
-      \end{axis}
-    \end{tikzpicture}
+\begin{frame}[fragile]{Rank Order Correlations of Dendrites Over Stimuli}
+\begin{center}
+	\begin{figure}\caption*{Weighted rank coefficient $\rho_{\omega}$ (todo: find more optimal weights)}
+      \includegraphics[width=1.0\textwidth]{rank_presence.png}
 	\end{figure}
-\end{frame}
-\begin{frame}{Bar charts}
-  \begin{figure}
-    \begin{tikzpicture}
-      \begin{axis}[
-        mbarplot,
-        xlabel={Foo},
-        ylabel={Bar},
-        width=0.9\textwidth,
-        height=6cm,
-      ]
-
-      \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
-      \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
-      \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};
-
-      \legend{lorem, ipsum, dolor}
-
-      \end{axis}
-    \end{tikzpicture}
-  \end{figure}
-\end{frame}
-\begin{frame}{Quotes}
-  \begin{quote}
-    Veni, Vidi, Vici
-  \end{quote}
+	\end{center}
 \end{frame}
 
-{%
-\setbeamertemplate{frame footer}{My custom footer}
-\begin{frame}[fragile]{Frame footer}
-    \themename defines a custom beamer template to add a text to the footer. It can be set via
-    \begin{verbatim}\setbeamertemplate{frame footer}{My custom footer}\end{verbatim}
-\end{frame}
-}
-
-\begin{frame}{References}
-  Some references to showcase [allowframebreaks] \cite{knuth92,ConcreteMath,Simpson,Er01,greenwade93}
+\begin{frame}[fragile]{DI and SVM Dendrtie Rank Order Correlation}
+\begin{center}
+	\begin{figure}
+	\caption*{Something is wrong here, should be more correlation}
+      \includegraphics[width=1.0\textwidth]{DI_vs_SVM.png}
+	\end{figure}
+	\end{center}
 \end{frame}
 
-\section{Conclusion}
-
-\begin{frame}{Summary}
-
-  Get the source of this theme and the demo presentation from
-
-  \begin{center}\url{github.com/matze/mtheme}\end{center}
-
-  The theme \emph{itself} is licensed under a
-  \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
-  Attribution-ShareAlike 4.0 International License}.
-
-  \begin{center}\ccbysa\end{center}
-
+\begin{frame}[fragile]{Tuning Curves}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{tuning.png}
+	\end{figure}
+	\end{center}
 \end{frame}
 
-{\setbeamercolor{palette primary}{fg=black, bg=yellow}
-\begin{frame}[standout]
-  Questions?
-\end{frame}
-}
-
-\appendix
-
-\begin{frame}[fragile]{Backup slides}
-  Sometimes, it is useful to add slides at the end of your presentation to
-  refer to during audience questions.
-
-  The best way to do this is to include the \verb|appendixnumberbeamer|
-  package in your preamble and call \verb|\appendix| before your backup slides.
-
-  \themename will automatically turn off slide numbering and progress bars for
-  slides in the appendix.
+\begin{frame}[fragile]{Tuning Curves}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{tuning_ca2+.png}
+      \caption*{todo:accuracies}
+	\end{figure}
+	\end{center}
 \end{frame}
 
-\begin{frame}[allowframebreaks]{References}
+\begin{frame}[fragile]{Behavoreal Prediction - Most Accurate Dendrites}
+\begin{table}
+    \caption*{Stimulus strength 1 (near thereshold)}
+    \begin{tabular}{c|c|c}
+      \toprule
+      Dendrite \# & Mean Accuracy & Standard Deviation\\
+      \midrule
+      70 & 0.78 & +/- 0.28\\
+      47 & 0.77 & +/- 0.32\\
+      56 & 0.73 & +/- 0.24\\
+      92 & 0.70 & +/- 0.33\\
+      \bottomrule
+    \end{tabular}
+  \end{table}
+\end{frame}
 
-  \bibliography{demo}
-  \bibliographystyle{abbrv}
+\begin{frame}[fragile]{Behavoreal Tuning}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{tuning_ca2+_bb.png}
+      \caption*{todo:accuracies}
+	\end{figure}
+	\end{center}
+\end{frame}
 
+\begin{frame}[fragile]{Rank Correlations of Behavoreal and Presence Dendrites}
+\begin{center}
+	\begin{figure}
+	\caption*{reduce ndends}
+      \includegraphics[width=1.0\textwidth]{transrank.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\section{Multivariate SMV Analysis}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites}
+Placeholder - Something wrong when using other files!
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavoreal}
+Placeholder - Something wrong when using other files!
+\end{frame}
+
+\begin{frame}[fragile]{Optimal Averaging Times}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{placeholder_wind_pres.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Optimal Averaging Times - Behavior}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{placeholder_wind_hit.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Mante - Approach (Placeholder Title)}
+Math goes here
+\end{frame}
+
+\begin{frame}[fragile]{Mante - Approach - Results}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{reg_norm_placeholder.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Mante - Approach - Results}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{reg_inte_placeholder.png}
+	\end{figure}
+	\end{center}
 \end{frame}

### 2017-07-12 rankcorr.py
asd

@@ -1,0 +1,21 @@
+import numpy as np
+
+def rW(R, Q):
+    n = R.shape[0]
+    return 1 - (6*np.sum((R-Q)**2 * ((np.ones(n)*n-R+np.ones(n)) + (np.ones(n)*n-Q+np.ones(n)))))/(n**4+n**3-n**2-n)
+
+def rFree(R, Q, W):
+    n = R.shape[0]
+    A = 1
+    B = -2/(np.sum(W*(np.ones(n)*n-2*np.arange(n)+np.ones(n))**2))
+    D = R-Q
+    
+    return A + B*np.sum(W*D**2)
+
+def rFree_sym(R, Q, W_r, W_q):
+    n = R.shape[0]
+    A = 1
+    B = -2/(np.sum(W_r*W_q*(np.ones(n)*n-2*np.arange(n)+np.ones(n))**2))
+    D = R-Q
+    
+    return A + B*np.sum(W_r*W_q*D**2)

### 2017-07-17 presentation/demo.tex
asd

@@
 \newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
+
+\usepackage{bibentry}
 
@@
 \begin{frame}[fragile]{The Experiment}
+Takahashi et al. 2016	
 \begin{columns}[T,onlytextwidth]
@@
 	\caption*{Trial-averaged $\text{Ca}^{2+}$ fluorescence traces of random dendrites}
-      \includegraphics[scale=0.35]{traces.png}
+      \includegraphics[width=\textwidth]{traces.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{The Data - Neuronal}
+	\begin{center}
+	\begin{figure}
+	\caption*{Trial-averaged $\text{Ca}^{2+}$ fluorescence traces of random dendrites}
+      \includegraphics[width=\textwidth]{traces_roi.png}
 	\end{figure}
@@
 	\begin{figure}
-      \includegraphics[scale=0.23	]{lickplots.png}
+      \includegraphics[width=\textwidth]{lickplot_single.png}
 	\end{figure}
@@
 	\begin{figure}
-      \includegraphics[scale=0.38]{psychometric.png}
+      \includegraphics[width=\textwidth]{psychometric.png}
 	\end{figure}
@@
 \only<+->{
-\item What information can we extract from the data?}
+\item What is the relationship between Ca2+ activity and stimulus intensity/behavior}
 \only<+->{
-\item What can we gain by doing multivariate analysis as opposed to univariate?}
-\only<+->{
-\item Can we say something about population coding?}
+\item Does a multivariate approach give us any significant advantage over a univariate one?}
 \end{itemize}
@@
 \begin{frame}[fragile]{Stimulus Presence Detection}
-\begin{itemize}
-\item Feature: mean activity of dendrite over one second after stimulus
-\item Class one: all trials with stimulus strength 0
-\item Class two: all trials with selected stimulus strength $(\neq 0)$
-\end{itemize}
+%\begin{itemize}
+%\item Feature: mean activity of dendrite over one second after stimulus
+%\item Class one: all trials with stimulus strength 0
+%\item Class two: all trials with selected stimulus strength $(\neq 0)$
+%\end{itemize}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{data_p.png}
+	\end{figure}
+	\end{center}
 \end{frame}
@@
 	\begin{figure}
-      \includegraphics[width=0.75\textwidth]{roc_max.png}
+      \includegraphics[width=1.0\textwidth]{roc_exp.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{ROC - Best ROC Curves}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{roc_four.png}
 	\end{figure}
@@
 
+\begin{frame}[fragile]{SVM - What is an SMV?}
+\begin{center}
+\only<+->{
+\begin{figure}
+      \includegraphics[height=0.3\textwidth]{svm_exp1.png}
+	\end{figure}}
+	\only<+->{
+	\begin{figure}
+      \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	\end{figure}}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Why SVM?}
+
+\begin{itemize}
+\item staple of machine learning
+\item regularization parameter limits overfitting
+\item good for small samples with many features (in theory)
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}[fragile]{SVM - Most Accurate Dendrites}
@@
 
+\begin{frame}[fragile]{Rank Order Correlation}
+\only<+->{
+We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$.}
+
+\only<+->{
+Standard approach: Spearman's rank order coefficient 
+$$
+\rho(R,Q) = 1 - \frac{6\sum_i^nD_i^2}{n(n	^2-1)}
+$$
+where $D_i=R_i-Q_i$.}
+
+\only<+->{
+Problem: Many of the dendrites are not significant for classification but affect $\rho$ greatly. We would like to be able to \textbf{weight our} $\mathbf{D_i}$'s.}
+\end{frame}
+
+\begin{frame}{Weighted Rank Order Correlation Coefficient}
+One possible soulution:
+$$
+\rho_W(R,Q) = 1-\frac{-2\sum_i^nw_iD_i^2}{\sum_i^nw_i(n-2i+1)^2}
+$$
+With a monotonicity constraint on $W$.
+\end{frame}
+
 \begin{frame}[fragile]{Rank Order Correlations of Dendrites Over Stimuli}
@@
       \includegraphics[width=1.0\textwidth]{rank_presence.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{DI and SVM Dendrtie Rank Order Correlation}
-\begin{center}
-	\begin{figure}
-	\caption*{Something is wrong here, should be more correlation}
-      \includegraphics[width=1.0\textwidth]{DI_vs_SVM.png}
 	\end{figure}
@@
 	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{tuning_ca2+.png}
-      \caption*{todo:accuracies}
+      \includegraphics[width=1.0\textwidth]{tuning_ca2+single.png}
 	\end{figure}
@@
 
-\begin{frame}[fragile]{Behavoreal Prediction - Most Accurate Dendrites}
+\begin{frame}[fragile]{Tuning Curves}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{tuning_ca2+.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Bevahior Detection}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{data_hm.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Behavioral Prediction - Most Accurate Dendrites}
 \begin{table}
-    \caption*{Stimulus strength 1 (near thereshold)}
+    \caption*{Different dataset - Stimulus strength 1 (near thereshold)}
     \begin{tabular}{c|c|c}
       \toprule
-      Dendrite \# & Mean Accuracy & Standard Deviation\\
+      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
       \midrule
-      70 & 0.78 & +/- 0.28\\
-      47 & 0.77 & +/- 0.32\\
-      56 & 0.73 & +/- 0.24\\
-      92 & 0.70 & +/- 0.33\\
+      88 & 0.80 & 0.08\\
+      57 & 0.80 & 0.08\\
+      92 & 0.78 & 0.06\\
+      56 & 0.76 & 0.10\\
       \bottomrule
@@
 
-\begin{frame}[fragile]{Behavoreal Tuning}
+\begin{frame}[fragile]{Behavorial Predition - Imbalance}
 \begin{center}
 	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{tuning_ca2+_bb.png}
-      \caption*{todo:accuracies}
+	  \caption*{$N_{no-lick}$ vs. $N_{lick}$ for all stimuli}
+      \includegraphics[width=1.0\textwidth]{fraction.png}
 	\end{figure}
@@
 
+%\begin{frame}[fragile]{Behavoreal Tuning}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{tuning_ca2+_bb.png}
+%      \caption*{todo:accuracies}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
 \begin{frame}[fragile]{Rank Correlations of Behavoreal and Presence Dendrites}
@@
 	\begin{figure}
-	\caption*{reduce ndends}
       \includegraphics[width=1.0\textwidth]{transrank.png}
@@
 
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites}
-Placeholder - Something wrong when using other files!
+\begin{frame}[fragile]{Presence Detection - Feature Selection}
+\only<+->{
+Since we have only few datapoints per condition (30-50 per class) in comparison to the number of features (100-150), we are prone to overfit to noise.}
+
+\only<+->{
+$\Rightarrow$ we have to do \textbf{feature selection}.}
+
+\only<+->{
+We can use the previously best discriminating dendrites (SVM/DI).}
 \end{frame}
 
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavoreal}
-Placeholder - Something wrong when using other files!
+\begin{frame}[fragile]{DI and SVM Dendrite Rank Order Correlation}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{rank_DI_SVM.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_presence.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_presence_alt.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_hitmiss.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_hitmiss_alt.png}
+	\end{figure}
+	\end{center}
 \end{frame}
@@
 	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=1.0\textwidth]{placeholder_wind_pres.png}
+	\caption*{Dummy}
+      \includegraphics[width=0.6\textwidth]{placeholder_wind_pres.png}
 	\end{figure}
@@
 	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=1.0\textwidth]{placeholder_wind_hit.png}
+	\caption*{Dummy}
+      \includegraphics[width=0.6\textwidth]{placeholder_wind_hit.png}
 	\end{figure}
@@
 
-\begin{frame}[fragile]{Mante - Approach (Placeholder Title)}
-Math goes here
-\end{frame}
+\section{Population Coding}
 
-\begin{frame}[fragile]{Mante - Approach - Results}
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
 \begin{center}
 	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=1.0\textwidth]{reg_norm_placeholder.png}
+      \includegraphics[width=1.0\textwidth]{coord.png}
 	\end{figure}
@@
 
-\begin{frame}[fragile]{Mante - Approach - Results}
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
 \begin{center}
 	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=1.0\textwidth]{reg_inte_placeholder.png}
+      \includegraphics[width=1.0\textwidth]{traj.png}
 	\end{figure}
@@
 
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{new_coord.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{trafo.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{trafo_final.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=0.7\textwidth]{reg.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=0.7\textwidth]{reg_sum.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}
+\begin{thebibliography}{9}
+\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016)
+\bibitem {mante} Mante V., Sussillo D., Shenoy KV., Newsome WT. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013)
+\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015)
+\end{thebibliography}
+\end{frame}
+
+\section*{Extra Slides}
+\begin{frame}[fragile]{Weighted Rank Order Correlation Coefficient}
+\only<+->{
+We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$.}
+
+\only<+->{
+Standard approach: Spearman's rank order coefficient 
+$$
+\rho(R,Q) = 1 - \frac{6\sum_i^nD_i^2}{n(n	^2-1)}
+$$
+where $D_i=R_i-Q_i$.}
+
+\only<+->{
+Problem: Many of the dendrites are not significant for classification but affect $\rho$ greatly. We would like to be able to \textbf{weight our} $\mathbf{D_i}$'s.}
+\end{frame}
+
+\begin{frame}[fragile]{Weighted Rank Order Correlation Coefficient}
+\only<+->{
+We want our rank order coefficient to be an affine linear function of $\sum_iw_iD_i^2$:
+
+$$
+\rho_W(R, Q) = A+B\sum_i^nw_iD_i^2
+$$}
+\only<+->{
+If $R=Q$, we want $\rho_W=1$, and if the rankings are reversed, we want $\rho_W=-1$.}
+
+\only<+->{
+The first condition gives us $A=1$, and the second one
+$$
+B=\frac{-2}{\sum_i^nw_i(n-2i+1)^2} 
+$$}
+\only<+->{
+Thus:
+$$
+\boxed{\rho_W(R,Q) = 1-\frac{-2\sum_i^nw_iD_i^2}{\sum_i^nw_i(n-2i+1)^2}}
+$$}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\only<+->{
+We would like to visualize the time evolution of the population response in a coordinate system in which the axes represent stimulus strength and choice.}
+
+\only<+->{
+To that end we use linear regression to write the normaized response of dendrite $i$ at time $t$ in trial $k$ as a linear combination of these task variables:
+$$
+r_k^{i,t} = \beta_1^{i,t}choice_k+\beta_2^{i,t}stimulus_k+\beta_3^{i,t}
+$$}
+
+\only<+->{
+The regression coefficients $\beta_{\nu}^{i,t}$ describe how much the activity of dendrite $i$ at time $t$ in trial $k$ corresponds with variable $\nu$.}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+We define
+$$
+\mathbf{F} = 
+\begin{bmatrix}
+choice_1 & ... & choice_n \\
+stimulus_1 & ... & stimulus_n \\
+1 & ... & 1
+\end{bmatrix}
+$$
+and estimate for each dendrite $i$ and timepoint $t$
+$$
+\boldsymbol{\beta^{i,t}} = \mathbf{(FF^T)^{-1}Fr^{i,t}}
+$$
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\only<+->{
+In total we have 14 conditions: 7 stimuli X two choices.}
+
+\only<+->{
+We define:
+$$
+\mathbf{x^{c,t}}
+$$
+as the (trial-averaged) population response to condition $c$ (for example lick at stimulus 1.00) at time $t$, which is a vector of $N_{unit}$ length.}
+
+\only<+->{
+The goal is to use $\boldsymbol{\beta}$ to find a two-dimensional subspace of the dendrite space into which we can transform $\mathbf{x^{c,t}}$.}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\only<+->{
+We then use PCA to denoise the data matrix
+$$
+\mathbf{X}=
+\begin{bmatrix}
+ &  &  & \\
+\mathbf{x_{c_1,t_1}} & ... & \mathbf{x_{c_1,t_n}} & ... & \mathbf{x_{c_m,t_n}}
+\\
+  &  &  &
+\end{bmatrix}
+$$}
+
+\only<+->{
+and we apply the denoising matrix to all $\boldsymbol{\beta^{\nu, t}}$ as well, which yields the denoised regression vectors
+$$
+\boldsymbol{\beta_{pca}^{\nu,t}}
+$$}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\only<+->{
+Since the $\boldsymbol{\beta_{pca}^{\nu,t}}$ are time variing but we would like a coordinate system that is fixed in time, we "freeze" them at the point in time at which there is maximum correlation:}
+\only<+->{
+\[
+\boldsymbol{\beta^{\nu}_{max}}=\boldsymbol{\beta_{pca}^{\nu,t^{\nu}_{max}}}
+\]
+\[
+t^{\nu}_{max} = argmax_t||\boldsymbol{\beta_{pca}^{\nu,t}}||
+\]}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\only<+->{
+We would like these $\boldsymbol{\beta^{\nu}_{max}}$ to be the basis vectors of our new coordinate system, however, they are not yet orthogonal.} 
+\only<+->{We fix this by applying QR-decomposition to 
+$$
+\mathbf{B^{max}}=
+\begin{bmatrix}
+\mathbf{\beta^1_{max}} & \mathbf{\beta^2_{max}}
+\end{bmatrix} = \mathbf{QR}
+$$
+where $\mathbf{Q}$ is an orthogonal matrix whose columns $\boldsymbol{\beta^{\nu}_{\bot}}$ are the \textbf{basis vectors} of our new coordinate system. We can now transform our data into it.}
+\end{frame}
+
 \end{document}

### 2017-07-18 presentation/demo.tex
asd

@@
 
+\begin{frame}[fragile]{SVM Specifics}
+\begin{itemize}
+\item All data are normalized to zero mean and unit variance
+\item Crossvalidation is performed to conrol for overfitting
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}[fragile]{SVM - Most Accurate Dendrites}
@@
 	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{data_p_tot.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
+Performance on global presence detection: \newline
+Mean: 0.68 \newline
+Standard deviation: 0.08
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{data_hm_tot.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
+Performance on global presence detection: \newline
+Mean: 0.71 \newline
+Standard deviation: 0.1
 \end{frame}

### 2017-07-19 presentation/demo.tex
asd

@@
 \only<+->{
+\item Can we build good classifiers for this data?}
+\only<+->{
 \item Does a multivariate approach give us any significant advantage over a univariate one?}
@@
 	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+	\begin{columns}[T,onlytextwidth]
+    \column{0.5\textwidth}
     	\only<+->{
       \begin{figure}
-      \includegraphics[height=0.3\textwidth]{svm_exp.png}
+      \includegraphics[height=0.7\textwidth]{svm_exp2.png}
       \end{figure}}
-	\end{center}
+
+    \column{0.5\textwidth}
+		\only<+->{
+      \begin{figure}
+      \includegraphics[height=0.7\textwidth]{svm_exp3.png}
+      \end{figure}}
+
+  \end{columns}
 \end{frame}
@@
   \end{table}
+\end{frame}
+
+\begin{frame}[fragile]{SVM - Numbers of Classifying Dendrites by Stimulus}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{n_acc.png}
+	\end{figure}
+	\end{center}
 \end{frame}
@@
 
+\begin{frame}[fragile]{Timing - What if we use different Averaging Windows?}
+So far we have always averaged over the first second after the stimulus. \newline
+
+What if we average over the second before or the second second after the stimulus?
+\end{frame}
+
+\begin{frame}[fragile]{Statistical Significance - Stimulus Presence}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Statistical Significance - Behavior}
+At threshold stimulus $\approx$ 1
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig_b.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
 \section{Multivariate SMV Analysis}
@@
 
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{data_hm_tot.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
-Performance on global presence detection: \newline
-Mean: 0.71 \newline
-Standard deviation: 0.1
-\end{frame}
-
 \begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection}
@@
 
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{data_hm_tot.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
+Performance on global presence detection: \newline
+Mean: 0.71 \newline
+Standard deviation: 0.1
+\end{frame}
+
 \begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
@@
       \includegraphics[width=1.0\textwidth]{combined_hitmiss_alt.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Optimal Averaging Times}
-\begin{center}
-	\begin{figure}
-	\caption*{Dummy}
-      \includegraphics[width=0.6\textwidth]{placeholder_wind_pres.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Optimal Averaging Times - Behavior}
-\begin{center}
-	\begin{figure}
-	\caption*{Dummy}
-      \includegraphics[width=0.6\textwidth]{placeholder_wind_hit.png}
 	\end{figure}

### 2017-08-01 presentation/demo.tex
asd

@@
 
-\title{Uni- and Multivariate Analysis of Dendritic Ca2+ Data}
-\subtitle{In a Stimulus Detection Task}
+\title{Dendritic Ca2+ as a Predictor of Stimulus Perception and Behavior}
+\subtitle{Uni- and Multivariate Analysis}
 \date{\today}
@@
 
-\begin{frame}{Table of contents}
-  \setbeamertemplate{section in toc}[sections numbered]
-  \tableofcontents[hideallsubsections]
-\end{frame}
+%\begin{frame}{Table of contents}
+%  \setbeamertemplate{section in toc}[sections numbered]
+%  \tableofcontents[hideallsubsections]
+%\end{frame}
 
@@
 
+\begin{frame}[fragile]{The Data - Behavioral}
+	\begin{center}
+	\begin{figure}
+      \includegraphics[width=\textwidth]{lickplot_single.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{The Data - Psychometric Curve}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=\textwidth]{psychometric.png}
+	\end{figure}
+	\end{center}
+
+\end{frame}
+
 \begin{frame}[fragile]{The Data - Neuronal}
@@
 
-\begin{frame}[fragile]{The Data - Behavioral}
-	\begin{center}
-	\begin{figure}
-      \includegraphics[width=\textwidth]{lickplot_single.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{The Data - Psychometric Curve}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=\textwidth]{psychometric.png}
-	\end{figure}
-	\end{center}
-
-\end{frame}
-
 \section{Goal}
@@
 \only<+->{
-\item Can we build good classifiers for this data?}
+\item Can we build predictive classifiers for this data?}
 \only<+->{
@@
 \section{Univariate Analysis}
+
+\begin{frame}[fragile]{SVM - What is an SVM?}
+\begin{columns}[T,onlytextwidth]
+\column{0.5\textwidth}
+\only<1->{
+\begin{center}
+\begin{figure}
+      \includegraphics[height=0.6\textwidth]{svm_exp1.png}
+	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\column{0.5\textwidth}
+\only<4->{
+SMVs...
+\begin{itemize}
+\item are a staple of machine learning
+\item have a regularization parameter that can combat overfitting
+\item are good for small samples with many features (in theory)
+\end{itemize}
+}
+\end{columns}
+	\begin{columns}[T,onlytextwidth]
+    \column{0.5\textwidth}
+    	\only<2->{
+      \begin{figure}
+      \includegraphics[height=0.7\textwidth]{svm_exp2.png}
+      \end{figure}}
+
+    \column{0.5\textwidth}
+		\only<3->{
+      \begin{figure}
+      \includegraphics[height=0.7\textwidth]{svm_exp3.png}
+      \end{figure}}
+
+  \end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Specifics}
+\begin{itemize}
+\only<+->{
+\item All data are normalized to zero mean and unit variance}
+\only<+->{
+\item Crossvalidation is performed to conrol for overfitting}
+\end{itemize}
+
+\end{frame}
 
@@
 \end{frame}
+
+\begin{frame}[fragile]{SVM - Most Accurate Dendrites}
+%\begin{table}
+%    \caption*{Stimulus strength 1 (near thereshold)}
+%    \begin{tabular}{c|c|c}
+%      \toprule
+%      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
+%      \midrule
+%      57 & 0.70 & 0.12\\
+%      53 & 0.68 & 0.14\\
+%      48 & 0.63 & 0.13\\
+%      27 & 0.62 & 0.08\\
+%      \bottomrule
+%    \end{tabular}
+%  \end{table}
+
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{presence_single.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+%\begin{frame}[fragile]{SVM - Numbers of Classifying Dendrites by Stimulus}
+%\begin{center}%
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{n_acc.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+\begin{frame}[fragile]{SVM - Statistical Significance}
+\begin{center}
+\only<+->{
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig_0.png}
+	\end{figure}}
+\only<+->{
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig_1.png}
+	\end{figure}}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Rank Order Correlation}
+\only<+->{
+We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$.}
+
+\only<+->{
+\begin{table}
+    \begin{tabular}{c|c|c|c|c}
+      \toprule
+      Dendrite & $R_i$ & $Q_i$ & $R_{acc}$ & $Q_{acc}$\\
+      \midrule
+      1 & 1 & 2 & 0.78 & 0.81\\
+      2 & 2 & 1 & 0.72 & 0.76\\
+      3 & 3 & 3 & 0.65 & 0.70\\
+      4 & 4 & 4 & 0.58 & 0.57\\
+      5 & 5 & 16 & 0.51 & 0.53\\
+      6 & 6 & 75 & 0.53 & 0.48\\
+      7 & 7 & 8 & 0.51 & 0.52\\
+      8 & 8 & 89 & 0.52 & 0.49\\
+      9 & 9 & 100 & 0.50 & 0.51\\
+      ... & ... & ... & ... & ...
+
+    \end{tabular}
+  \end{table}
+}
+\end{frame}
+
+\begin{frame}[fragile]{Rank Order Correlation}
+\only<+->{
+Standard approach: \textbf{Spearman's rank order coefficient} 
+$\boldsymbol{\rho}$}
+
+\only<+->{
+$$
+\rho(R,Q) = 1 - \frac{6\sum_i^nD_i^2}{n(n	^2-1)}
+$$
+}
+
+\only<+->{
+Problem: Many of the dendrites are not significant for classification but affect $\rho$ greatly. We would like to be able to \textbf{weight our} $\mathbf{R}$'s and $\mathbf{Q}$'s.}
+\end{frame}
+
+\begin{frame}{Weighted Rank Order Correlation Coefficient}
+One possible solution:
+$$
+\rho_W(R,Q) = 1-\frac{-2\sum_i^nw_iD_i^2}{\sum_i^nw_i(n-2i+1)^2}
+$$
+With a monotonicity constraint on $W$.
+\end{frame}
+
+\begin{frame}[fragile]{Rank Order Correlations of Dendrites Over Stimuli}
+
+	\begin{columns}[T,onlytextwidth]
+    \column{0.5\textwidth}
+    \begin{center}
+    \only<+->{
+	\begin{figure}
+	\caption*{Experiment 1}
+      \includegraphics[width=1.0\textwidth]{rank_presence_0.png}
+	\end{figure}}
+	\end{center}
+	\column{0.5\textwidth}
+	\begin{center}
+	\only<+->{
+	\begin{figure}
+	\caption*{Experiment 2}
+      \includegraphics[width=1.0\textwidth]{rank_presence.png}
+	\end{figure}}
+	\end{center}
+	\end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{Responses of One Dendrite to Different Stimuli}
+
+	\begin{columns}[T,onlytextwidth]
+    \column{0.5\textwidth}
+    \begin{center}
+    \only<+->{
+	\begin{figure}
+	\caption*{Experiment 1}
+      \includegraphics[width=1.0\textwidth]{tuning_ca2+_single_0.png}
+	\end{figure}}
+	\end{center}
+	\column{0.5\textwidth}
+	\begin{center}
+	\only<+->{
+	\begin{figure}
+	\caption*{Experiment 2}
+      \includegraphics[width=1.3\textwidth]{tuning_ca2+single.png}
+	\end{figure}}
+	\end{center}
+	\end{columns}
+\end{frame}
+
+%\begin{frame}[fragile]{Tuning Curves}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{tuning_ca2+single.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+%\begin{frame}[fragile]{Tuning Curves}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{tuning_ca2+.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+\begin{frame}[fragile]{Behavior Detection}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{data_hm.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Behavioral Prediction - Most Accurate Dendrites}
+\begin{table}
+    \caption*{Different dataset - Stimulus strength 1 (near thereshold)}
+    \begin{tabular}{c|c|c}
+      \toprule
+      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
+      \midrule
+      88 & 0.80 & 0.08\\
+      57 & 0.80 & 0.08\\
+      92 & 0.78 & 0.06\\
+      56 & 0.76 & 0.10\\
+      \bottomrule
+    \end{tabular}
+  \end{table}
+\end{frame}
+
+\begin{frame}[fragile]{Behavioral Predition - Imbalance}
+\begin{center}
+	\begin{figure}
+	  \caption*{$N_{no-lick}$ vs. $N_{lick}$ for all stimuli}
+      \includegraphics[width=1.0\textwidth]{fraction.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+%\begin{frame}[fragile]{Behavoreal Tuning}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{tuning_ca2+_bb.png}
+%      \caption*{todo:accuracies}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+\begin{frame}[fragile]{Rank Order Correlations of Best Behavior and Presence Dendrites}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{tranksrank_3x3.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Timing - What if We Use Different Averaging Windows?}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{timing_exp.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Timing - Statistical Significance}
+\begin{center}
+\only<+->{
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig_t0.png}
+	\end{figure}}
+\only<+->{
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig_t1.png}
+	\end{figure}}
+	\end{center}
+\end{frame}
+
+%\begin{frame}[fragile]{Statistical Significance - Stimulus Presence}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{statsig.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+\begin{frame}[fragile]{Statistical Significance - Behavior}
+At threshold stimulus $\approx$ 1
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{statsig_b.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\section{Multivariate SMV Analysis}
+
+\begin{frame}[fragile]{Presence Detection - Feature Selection}
+\only<+->{
+Since we have fewer datapoints per condition (30-50 per class) than features (100-150), we are prone to overfit to noise (which is abundant in our data).}
+
+\only<+->{
+$\Rightarrow$ we have to do \textbf{feature selection}.}
+
+\only<+->{
+We can use the previously best discriminating dendrites.}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection, Experiment 1}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{combined_presence_0.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_hitmiss.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\section{Population Coding}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{coord.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{traj.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{new_coord.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+%\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{trafo.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{trafo_final.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{reg.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{reg_sum.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Conclusions}
+\begin{itemize}
+\item We can build high accuracy classifiers based on this data
+\item Multivariate analysis is advantageous
+\item Prestimulus Ca2+ activity does not predict the animal's decision
+\item Different dendrites code for stimulus and behavior
+\item There are very large differences between different animals/experiments
+\item We need more data - particularily for multivariate analysis
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\begin{thebibliography}{9}
+\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016)
+\bibitem {mante} Mante V., Sussillo D., Shenoy KV., Newsome WT. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013)
+\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015)
+\end{thebibliography}
+\end{frame}
+
+\section*{Extra Slides}
 
@@
 
-\begin{frame}[fragile]{$\text{Ca}^{2+}$-Trace of Largest $|\text{DI}|$-Dendrites}
+\begin{frame}[fragile]{$\text{Ca}^{2+}$-Traces of Largest $|\text{AUC}-0.5|$-Dendrites}
 \begin{center}
@@
 
-\begin{frame}[fragile]{SVM - What is an SMV?}
-\begin{center}
-\only<+->{
-\begin{figure}
-      \includegraphics[height=0.3\textwidth]{svm_exp1.png}
-	\end{figure}}
-	%\only<+->{
-	%\begin{figure}
-    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
-	%\end{figure}}
-	\end{center}
-	\begin{columns}[T,onlytextwidth]
-    \column{0.5\textwidth}
-    	\only<+->{
-      \begin{figure}
-      \includegraphics[height=0.7\textwidth]{svm_exp2.png}
-      \end{figure}}
-
-    \column{0.5\textwidth}
-		\only<+->{
-      \begin{figure}
-      \includegraphics[height=0.7\textwidth]{svm_exp3.png}
-      \end{figure}}
-
-  \end{columns}
-\end{frame}
-
-\begin{frame}[fragile]{Why SVM?}
-
-\begin{itemize}
-\item staple of machine learning
-\item regularization parameter limits overfitting
-\item good for small samples with many features (in theory)
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]{SVM Specifics}
-\begin{itemize}
-\item All data are normalized to zero mean and unit variance
-\item Crossvalidation is performed to conrol for overfitting
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]{SVM - Most Accurate Dendrites}
-\begin{table}
-    \caption*{Stimulus strength 1 (near thereshold)}
-    \begin{tabular}{c|c|c}
-      \toprule
-      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
-      \midrule
-      57 & 0.70 & 0.12\\
-      53 & 0.68 & 0.14\\
-      48 & 0.63 & 0.13\\
-      27 & 0.62 & 0.08\\
-      \bottomrule
-    \end{tabular}
-  \end{table}
-\end{frame}
-
-\begin{frame}[fragile]{SVM - Numbers of Classifying Dendrites by Stimulus}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{n_acc.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Rank Order Correlation}
-\only<+->{
-We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$.}
-
-\only<+->{
-Standard approach: Spearman's rank order coefficient 
-$$
-\rho(R,Q) = 1 - \frac{6\sum_i^nD_i^2}{n(n	^2-1)}
-$$
-where $D_i=R_i-Q_i$.}
-
-\only<+->{
-Problem: Many of the dendrites are not significant for classification but affect $\rho$ greatly. We would like to be able to \textbf{weight our} $\mathbf{D_i}$'s.}
-\end{frame}
-
-\begin{frame}{Weighted Rank Order Correlation Coefficient}
-One possible soulution:
-$$
-\rho_W(R,Q) = 1-\frac{-2\sum_i^nw_iD_i^2}{\sum_i^nw_i(n-2i+1)^2}
-$$
-With a monotonicity constraint on $W$.
-\end{frame}
-
-\begin{frame}[fragile]{Rank Order Correlations of Dendrites Over Stimuli}
-\begin{center}
-	\begin{figure}\caption*{Weighted rank coefficient $\rho_{\omega}$ (todo: find more optimal weights)}
-      \includegraphics[width=1.0\textwidth]{rank_presence.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
 \begin{frame}[fragile]{Tuning Curves}
@@
 
-\begin{frame}[fragile]{Tuning Curves}
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection, Experiment 2}
 \begin{center}
 	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{tuning_ca2+single.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Tuning Curves}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{tuning_ca2+.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Bevahior Detection}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{data_hm.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Behavioral Prediction - Most Accurate Dendrites}
-\begin{table}
-    \caption*{Different dataset - Stimulus strength 1 (near thereshold)}
-    \begin{tabular}{c|c|c}
-      \toprule
-      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
-      \midrule
-      88 & 0.80 & 0.08\\
-      57 & 0.80 & 0.08\\
-      92 & 0.78 & 0.06\\
-      56 & 0.76 & 0.10\\
-      \bottomrule
-    \end{tabular}
-  \end{table}
-\end{frame}
-
-\begin{frame}[fragile]{Behavorial Predition - Imbalance}
-\begin{center}
-	\begin{figure}
-	  \caption*{$N_{no-lick}$ vs. $N_{lick}$ for all stimuli}
-      \includegraphics[width=1.0\textwidth]{fraction.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-%\begin{frame}[fragile]{Behavoreal Tuning}
-%\begin{center}
-%	\begin{figure}
-%      \includegraphics[width=1.0\textwidth]{tuning_ca2+_bb.png}
-%      \caption*{todo:accuracies}
-%	\end{figure}
-%	\end{center}
-%\end{frame}
-
-\begin{frame}[fragile]{Rank Correlations of Behavoreal and Presence Dendrites}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{transrank.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Timing - What if we use different Averaging Windows?}
-So far we have always averaged over the first second after the stimulus. \newline
-
-What if we average over the second before or the second second after the stimulus?
-\end{frame}
-
-\begin{frame}[fragile]{Statistical Significance - Stimulus Presence}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{statsig.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Statistical Significance - Behavior}
-At threshold stimulus $\approx$ 1
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{statsig_b.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\section{Multivariate SMV Analysis}
-
-\begin{frame}[fragile]{Presence Detection - Feature Selection}
-\only<+->{
-Since we have only few datapoints per condition (30-50 per class) in comparison to the number of features (100-150), we are prone to overfit to noise.}
-
-\only<+->{
-$\Rightarrow$ we have to do \textbf{feature selection}.}
-
-\only<+->{
-We can use the previously best discriminating dendrites (SVM/DI).}
-\end{frame}
-
-\begin{frame}[fragile]{DI and SVM Dendrite Rank Order Correlation}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{rank_DI_SVM.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
       \includegraphics[width=1.0\textwidth]{combined_presence.png}
@@
 
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{data_p_tot.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
-Performance on global presence detection: \newline
-Mean: 0.68 \newline
-Standard deviation: 0.08
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{combined_presence_alt.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{combined_hitmiss.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{data_hm_tot.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
-Performance on global presence detection: \newline
-Mean: 0.71 \newline
-Standard deviation: 0.1
-\end{frame}
-
-\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
-\begin{center}
-	\begin{figure}
-	%\caption*{todo: tens, improve weights}
-      \includegraphics[width=1.0\textwidth]{combined_hitmiss_alt.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\section{Population Coding}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{coord.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{traj.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{new_coord.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{trafo.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{trafo_final.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Response in Task Variable Space}
-\begin{center}
-	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=0.7\textwidth]{reg.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Response in Task Variable Space}
-\begin{center}
-	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=0.7\textwidth]{reg_sum.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}
-\begin{thebibliography}{9}
-\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016)
-\bibitem {mante} Mante V., Sussillo D., Shenoy KV., Newsome WT. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013)
-\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015)
-\end{thebibliography}
-\end{frame}
-
-\section*{Extra Slides}
 \begin{frame}[fragile]{Weighted Rank Order Correlation Coefficient}
@@
 
+\begin{frame}[fragile]{DI and SVM Dendrite Rank Order Correlation}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{rank_DI_SVM.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{data_p_tot.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
+Performance on global presence detection: \newline
+Mean: 0.68 \newline
+Standard deviation: 0.08
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Presence Detection}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_presence_alt.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{data_hm_tot.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
+Performance on global presence detection: \newline
+Mean: 0.71 \newline
+Standard deviation: 0.1
+\end{frame}
+
+\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavioral}
+\begin{center}
+	\begin{figure}
+	%\caption*{todo: tens, improve weights}
+      \includegraphics[width=1.0\textwidth]{combined_hitmiss_alt.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
 \end{document}

### 2017-08-03 SVM_final.py
for Filip

@@ -1,0 +1,394 @@
+import h5py
+import numpy as np
+from sklearn import svm
+from sklearn.model_selection import cross_val_score
+from sklearn import preprocessing
+from smooth import smoothen
+from sklearn.decomposition import PCA
+
+def SVM_presence_single(filename, amp, svm_kernel='linear', cv=5, scoring='accuracy'):
+    '''
+    Trains an SVM on the Ca2+ data of single dendrites to detect stimulus presence.
+    
+    filename: string, name of experiment file
+    amp: float, stimulus strength, must exist
+    svm_kernel: string, specifies svm kernel to use for training
+    cv: int, number of folds for cv
+    scoring: only use accuracy!
+    
+    returns: n_dendrites x cv ndarray. Each row holds the accuracy values for each fold for one dendrite.
+    '''
+    f = h5py.File(filename+".hdf5", "r")
+    data = f['data']
+    meta = f['meta']
+    g = h5py.File(filename[:-6]+"roi.hdf5", "r")
+    motion_mask = (g['inFrameDend'][:].astype(bool)).reshape(g['inFrameDend'].shape[0])
+    #load data
+
+    stims = np.unique(meta[:,1])[1:]        #exclude zero-stim-trials
+    assert(amp in list(stims)), "this stimAmp was not used in chosen experiment. Cose one from {}.".format(stims)
+    #load stimAmps and check whether the chosen amp matches one of them
+
+    clf = svm.SVC(kernel=svm_kernel)
+    #create classifier
+    
+    #n_dendrites = data.shape[1]
+    n_dendrites = np.sum(motion_mask)
+    #number of dendrites, loop over these
+    
+    sc = np.zeros((n_dendrites, cv))
+    #will later hold the cv-scores
+    
+    for site in range(n_dendrites):
+        baseline = np.mean(data[:,motion_mask,:58], axis=2).reshape(data.shape[0], data[:,motion_mask,:].shape[1], 1)
+        #baselibe for every trial is the mean over the first second - 58 frames
+        
+        mn_dnd_chng = np.mean(data[:,motion_mask,58:116]-baseline, axis=2)
+        #mean dendritic change = second second minus baseline, mean
+
+        present_mask = meta[:,1]==amp
+        absent_mask = meta[:,1]==0
+        #boolean masks of the trials where stimAmp==amp and stimAmp==0
+
+        trials_mask = np.logical_or(present_mask, absent_mask)
[…]

### 2017-08-03 rankcorr.py
added comment strings to rankcorr

@@ -1,10 +1,16 @@
 import numpy as np
 
 def rW(R, Q):
+    '''
+    Linearily weighted rank-order correlation between two orderings R and Q
+    '''
     n = R.shape[0]
     return 1 - (6*np.sum((R-Q)**2 * ((np.ones(n)*n-R+np.ones(n)) + (np.ones(n)*n-Q+np.ones(n)))))/(n**4+n**3-n**2-n)
 
 def rFree(R, Q, W):
+    '''
+    Weighted rank-order correlation between two orderings R and Q with weights W. Weights should be monotonous.
+    '''
     n = R.shape[0]
     A = 1
     B = -2/(np.sum(W*(np.ones(n)*n-2*np.arange(n)+np.ones(n))**2))
@@ -13,6 +19,9 @@ def rFree(R, Q, W):
     return A + B*np.sum(W*D**2)
 
 def rFree_sym(R, Q, W_r, W_q):
+    '''
+    Weighted rank-order correlation between two orderings R and Q with weights W_r, W_q whose product is used. 
+    '''
     n = R.shape[0]
     A = 1
     B = -2/(np.sum(W_r*W_q*(np.ones(n)*n-2*np.arange(n)+np.ones(n))**2))

### 2017-09-13 presentation_Naoya/demo.tex
asd

--- 2017-08-01 presentation/demo.tex
@@
 \section{Univariate Analysis}
-
 \begin{frame}[fragile]{SVM - What is an SVM?}
@@
 \column{0.5\textwidth}
-\only<1->{
 \begin{center}
 \begin{figure}
-      \includegraphics[height=0.6\textwidth]{svm_exp1.png}
+      \includegraphics[height=0.6\textwidth]{machine_learning.png}
+      \caption*{Figure - xkcd}
+	\end{figure}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\column{0.5\textwidth}
+SMV...
+\begin{itemize}
+\item is a supervised learning algorithm
+\begin{itemize}
+\item uses labelled data
+\end{itemize}
+\item has a regularization parameter that can combat overfitting
+\item is good for small samples with many features (in theory)
+\end{itemize}
+\end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{SVM - What is an SVM?}
+\only<1->{
+Works on linearily separable and nonseparable data of \textbf{arbitrary dimension}}
+\begin{columns}[T,onlytextwidth]
+\column{0.5\textwidth}
+\begin{center}
+\only<2->{
+\begin{figure}
+      \includegraphics[height=0.8\textwidth]{svm_sep.png}
 	\end{figure}}
@@
 \column{0.5\textwidth}
-\only<4->{
-SMVs...
-\begin{itemize}
-\item are a staple of machine learning
-\item have a regularization parameter that can combat overfitting
-\item are good for small samples with many features (in theory)
-\end{itemize}
-}
+\begin{center}
+\only<3->{
+\begin{figure}
+      \includegraphics[height=0.8\textwidth]{svm_nonsep.png}
+	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
 \end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{SVM - What is an SVM? Linearily Separable Case}
+\begin{columns}[T,onlytextwidth]
+\column{0.4\textwidth}
+\begin{center}
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+There are many separating hyperplanes, but which one is best?
+\end{center}
+\column{0.55\textwidth}
+\begin{center}
+\begin{figure}
+      \includegraphics[height=0.9\textwidth]{svm_hyper.png}
+	\end{figure}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
+\begin{columns}[T,onlytextwidth]
+\column{0.4\textwidth}
+\only<+->{
+\begin{center}
+\bigskip
+\bigskip
+\bigskip
+The one that maximizes the hyperplanes' distance from the nearest datapoints of either class while classifying all data correctly - \textbf{the margin}
+\end{center}}
+\column{0.55\textwidth}
+\begin{center}
+\only<+->{
+\begin{figure}
+      \includegraphics[height=0.9\textwidth]{svm_mar.png}
+	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
+\begin{columns}[T,onlytextwidth]
+\column{0.4\textwidth}
+\begin{center}
+\only<+->{
+The hyperplane is given by
+\begin{align*}
+g(\mathbf{x}) = \mathbf{w^Tx + b}
+\end{align*}}
+\only<+->{
+It turns out that the margin is given by $\frac{2}{||w||}$ and we maximize it by minimizing
+\begin{align*}
+\frac{1}{2}||\mathbf{w}||_2^2
+\end{align*}}
+\only<+->{
+under the constraint that \textbf{all data are classified correctly}.}
+\end{center}
+\column{0.55\textwidth}
+\begin{center}
+\begin{figure}
+      \includegraphics[height=0.9\textwidth]{svm_mar.png}
+	\end{figure}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\end{columns}
+\end{frame}
+
+\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
 \begin{columns}[T,onlytextwidth]
 \column{0.5\textwidth}
-    	\only<2->{
+\begin{center}
+\only<+->{
 \begin{figure}
-      \includegraphics[height=0.7\textwidth]{svm_exp2.png}
+      \includegraphics[height=0.8\textwidth]{svm_nonsep.png}
 	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\column{0.5\textwidth}
+\begin{center}
+\only<+->{
+\begin{figure}
+      \includegraphics[height=0.8\textwidth]{svm_cl.png}
+	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\end{columns}
+\end{frame}
 
+\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
+\only<+->{
+We permit Errors, but still penalize them!}
+\begin{columns}[T,onlytextwidth]
 \column{0.5\textwidth}
-		\only<3->{
+\begin{center}
+\only<+->{
 \begin{figure}
-      \includegraphics[height=0.7\textwidth]{svm_exp3.png}
+      \includegraphics[height=0.8\textwidth]{svm_nonsep_mar.png}
 	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\column{0.5\textwidth}
+\begin{center}
+\only<+->{
+\begin{figure}
+      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
+	\end{figure}}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
+\end{columns}
+\end{frame}
 
+\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
+\begin{columns}[T,onlytextwidth]
+\column{0.5\textwidth}
+\only<+->{
+Instead of $\frac{1}{2}||\mathbf{w}||_2^2$ we now minimize
+\begin{align*}
+\frac{1}{2}||\mathbf{w}||_2^2 + C\sum_{i=1}^n \xi_i}
+\end{align*}
+\only<+->{
+where $\xi_i$ is the distance of a data point from their correct decision region.}
+
+\only<+->{
+\textbf{The parameter C lets us now control the tradeoff between the generalization and training error (overfitting).}}
+\column{0.5\textwidth}
+\begin{center}
+\begin{figure}
+      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
+	\end{figure}
+	%\only<+->{
+	%\begin{figure}
+    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+	%\end{figure}}
+	\end{center}
 \end{columns}
@@
 \only<+->{
-We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$.}
+We want to quantify the similarity between two rank orders of dendrites $R$ and $Q$, which both have length $n$. For example, we would like to see whether similar dendrites react to similar stimuli.}
 
@@
 \only<+->{
-$$
-\rho(R,Q) = 1 - \frac{6\sum_i^nD_i^2}{n(n	^2-1)}
-$$
-}
-
-\only<+->{
-Problem: Many of the dendrites are not significant for classification but affect $\rho$ greatly. We would like to be able to \textbf{weight our} $\mathbf{R}$'s and $\mathbf{Q}$'s.}
-\end{frame}
-
-\begin{frame}{Weighted Rank Order Correlation Coefficient}
-One possible solution:
-$$
-\rho_W(R,Q) = 1-\frac{-2\sum_i^nw_iD_i^2}{\sum_i^nw_i(n-2i+1)^2}
-$$
-With a monotonicity constraint on $W$.
+We use a modified version of that because we usually have \textbf{many uninformative dendrites} that can skew the result (their exact rank is unimportant).}
 \end{frame}
@@
 
-\section{Multivariate SMV Analysis}
+\section{Multivariate SVM Analysis}
 
@@
       \includegraphics[width=1.0\textwidth]{combined_hitmiss.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\section{Population Coding}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{coord.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{traj.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{new_coord.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-%\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-%\begin{center}
-%	\begin{figure}
-%      \includegraphics[width=1.0\textwidth]{trafo.png}
-%	\end{figure}
-%	\end{center}
-%\end{frame}
-
-\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
-\begin{center}
-	\begin{figure}
-      \includegraphics[width=1.0\textwidth]{trafo_final.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Response in Task Variable Space}
-\begin{center}
-	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=1.0\textwidth]{reg.png}
-	\end{figure}
-	\end{center}
-\end{frame}
-
-\begin{frame}[fragile]{Population Response in Task Variable Space}
-\begin{center}
-	\begin{figure}
-	\caption*{Solve Problem with combined SVM first}
-      \includegraphics[width=1.0\textwidth]{reg_sum.png}
 	\end{figure}
@@
 $$}
+\end{frame}
+
+\begin{frame}{Weighted Rank Order Correlation Coefficient}
+One possible solution:
+$$
+\rho_W(R,Q) = 1-\frac{-2\sum_i^nw_iD_i^2}{\sum_i^nw_i(n-2i+1)^2}
+$$
+With a monotonicity constraint on $W$.
 \end{frame}
@@
 
+\section{Population Coding}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{coord.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{traj.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{new_coord.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+%\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+%\begin{center}
+%	\begin{figure}
+%      \includegraphics[width=1.0\textwidth]{trafo.png}
+%	\end{figure}
+%	\end{center}
+%\end{frame}
+
+\begin{frame}[fragile]{Population Coding - Idea (Mante, Sussillo 2013)}
+\begin{center}
+	\begin{figure}
+      \includegraphics[width=1.0\textwidth]{trafo_final.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{reg.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
+\begin{frame}[fragile]{Population Response in Task Variable Space}
+\begin{center}
+	\begin{figure}
+	\caption*{Solve Problem with combined SVM first}
+      \includegraphics[width=1.0\textwidth]{reg_sum.png}
+	\end{figure}
+	\end{center}
+\end{frame}
+
 \end{document}

### 2017-09-13 presentation_Naoya/demo.tex
asd

@@
 \only<+->{
-\item What is the relationship between Ca2+ activity and stimulus intensity/behavior}
+\item What is the relationship between Ca2+ activity and stimulus intensity/behavior?}
 \only<+->{
@@
 \bigskip
-The one that maximizes the hyperplanes' distance from the nearest datapoints of either class while classifying all data correctly - \textbf{the margin}
+The one that maximizes the hyperplane's distance from the nearest datapoints of either class while classifying all data correctly - \textbf{the margin}
 \end{center}}
@@
 \only<+->{
-The hyperplane is given by
-\begin{align*}
-g(\mathbf{x}) = \mathbf{w^Tx + b}
-\end{align*}}
-\only<+->{
-It turns out that the margin is given by $\frac{2}{||w||}$ and we maximize it by minimizing
-\begin{align*}
-\frac{1}{2}||\mathbf{w}||_2^2
-\end{align*}}
-\only<+->{
-under the constraint that \textbf{all data are classified correctly}.}
+Maximization of the margin can be formulated as a \textbf{constrained minimization problem}!
+
+}
+%\only<+->{
+%The hyperplane is given by
+%\begin{align*}
+%g(\mathbf{x}) = \mathbf{w^Tx + b}
+%\end{align*}}
+%\only<+->{
+%It turns out that the margin is given by $\frac{2}{||w||}$ and we maximize it by minimizing
+%\begin{align*}
+%\frac{1}{2}||\mathbf{w}||_2^2
+%\end{align*}}
+%\only<+->{
+%\bigskip
+%\bigskip
+%With the constraint that \textbf{all data are classified correctly}.}
 \end{center}
@@
 \only<+->{
-We permit Errors, but still penalize them!}
+We permit errors, but still penalize them!}
 \begin{columns}[T,onlytextwidth]
@@
 
+%\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
+%\begin{columns}[T,onlytextwidth]
+%\column{0.5\textwidth}
+%\only<+->{
+%Instead of $\frac{1}{2}||\mathbf{w}||_2^2$ we now minimize
+%\begin{align*}
+%\frac{1}{2}||\mathbf{w}||_2^2 + C\sum_{i=1}^n \xi_i}
+%\end{align*}
+%\only<+->{
+%where $\xi_i$ is the distance of a data point from their correct decision region.}
+%
+%\only<+->{
+%\textbf{The parameter C lets us now control the tradeoff between the generalization and training error (overfitting).}}
+%\column{0.5\textwidth}
+%\begin{center}
+%\begin{figure}
+%      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
+%	\end{figure}
+%	%\only<+->{
+%	%\begin{figure}
+%    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
+%	%\end{figure}}
+%	\end{center}
+%\end{columns}
+%\end{frame}
+
 \begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
@@
 \only<+->{
-Instead of $\frac{1}{2}||\mathbf{w}||_2^2$ we now minimize
-\begin{align*}
-\frac{1}{2}||\mathbf{w}||_2^2 + C\sum_{i=1}^n \xi_i}
-\end{align*}
+We can still formulate this as a constrained minimization problem, but now we \textbf{minimize the sum of errors while maximizing the margin}.}
 \only<+->{
-where $\xi_i$ is the distance of a data point from their correct decision region.}
 
-\only<+->{
-\textbf{The parameter C lets us now control the tradeoff between the generalization and training error (overfitting).}}
+\bigskip
+The coefficient $C$ controls the width of the margin at the expense of worse separation during training.}
 \column{0.5\textwidth}
@@
 \only<+->{
-\item Crossvalidation is performed to conrol for overfitting}
+\item Crossvalidation is performed to control for overfitting}
 \end{itemize}
@@
 \begin{table}
-    \caption*{Different dataset - Stimulus strength 1 (near thereshold)}
+    \caption*{Different dataset - Stimulus strength 1 (near threshold)}
     \begin{tabular}{c|c|c}
@@
 \begin{thebibliography}{9}
-\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016)
-\bibitem {mante} Mante V., Sussillo D., Shenoy KV., Newsome WT. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013)
-\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015)
+\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016).
+\bibitem {mante} Mante V., Sussillo D., Shenoy, K. V., Newsome, W. T. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013).
+\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015).
 \end{thebibliography}
